Import_Map

### 2024-06-05 Output/PLOSRound2/ResponsetoReviewers.txt

PONE-D-24-11318
Prochlorococcus marinus responses to light and oxygen
PLOS ONE

Jos? A. Fern?ndez Robledo, Ph.D. 
Academic Editor 
PLOS ONE

Dear Dr. Fern?ndez Robledo,

We thank you and the reviewers for constructive feedback, which we have addressed through extensive revisions, outlined below, which we believe have improved the manuscript.

@@

209: It seems overly general to blame the culturing difficulties solely on having reduced genomes ? in 
this context, it is the lack of just one gene (catalase) that matters, and reduced genomes reflect an 
outcome of the ultimate suite of selective pressures acting on these systems.

Thank you for your comment. We edited the text in the revised manuscript: "*Prochlorococcus marinus* remain challenging to culture at high densities or under fluctuating environments, partially due to their dependence upon mutualistic heterotrophic bacteria to detoxify
reactive oxygen species [48,49]." 
Line XXX:

363: Could the authors comment somewhere on why you took this proteomic approach to examine the 
baseline distribution of Pro across O2 and depth, as opposed to (or at least in concert with) the 
extensive metagenomic, amplicon, qPCR, etc datasets of ecotype abundances available?

Thank you for your comment. Co-authors, Aurora Mattison and Dr. Amanda Cockshutt, used the metaproteomics database as an extension of their earlier studies on the functional implications of differential protein allocations across different Prochlorococcus strains [Zorz et al. 2015, Bonisteel et al. 2018]. Those studies indeed motivated the design of our growth matrix. Extending the study to include metagonomic analyses is valid but is beyond our scope.
We edited the text in the revised manuscript: "Our analyses utilized a proteomics dataset; however, alternate approaches, such as metagenomics or metatranscriptomics, could have been employed to analyze ecotype abundances using the TARA Oceans [@pesantOpenScienceResources2015] dataset."
Line: XXX

### 2024-06-05 Code/Plots_ProNicheMap.Rmd
Doug looked at map code
depth photoperiod .Rds summary read in
condition table for strain distributions

----------------------------------------Create map ----------------------------------------------

@@

```{r}
world_coordinates <- map_data("world")

world_coordinates$facetsPresent <- 'Present'
world_coordinates$facetsFuture <- 'Future~scenario'

data_textA <- data.frame(label = c('A'))
data_textB <- data.frame(label = c('B'))
data_textC <- data.frame(label = c('C'))
data_textD <- data.frame(label = c('D'))
```

>>>>

```{r read photoperiod depth data}
PhotoperiodDepth <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthPhotoperiodTableFilter.Rds"))

PhotoperiodDepthOMZ <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  relocate(DepthNames, .after = lat) |>
  mutate(CladeHLI = 1,
         CladeLLII_LLIII = 1,
         CladeLLIV = 1)

PhotoperiodDepthOMZ

PhotoperiodDepthFullO2 <- PhotoperiodDepth |>
  select(-c(ToD, DepthPARabs, DepthPARSine, DepthPARabsNA, Photicperiod:PhoticperiodSineSatPAR_h)) |>
  filter(DepthNames %in% c("50 m", "100 m")) |>
  relocate(DepthNames, .after = lat) |>
   mutate(CladeHLI = 1,
         CladeLLII_LLIII = 1,
         CladeLLIV = 1)

PhotoperiodDepthFullO2

```{r read spectral depth backdrop}
DepthBackdrop <- readRDS(file = file.path("..", "Data", "ProcessedData", "DepthBackdrop.Rds"))

DepthBackdrop 
```

@@

```{r world map}
world_coordinates <- map_data("world")

world_coordinates$facetsFuture <- 'Future~scenario'

data_textA <- data.frame(label = c('A'))
data_textB <- data.frame(label = c('B'))
data_textC <- data.frame(label = c('C'))
```
